### 2019-06-12 2-Chapters/2-Chapter/chapter2.tex
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

\paragraph{About Markov models.}
%
% Markov models: we do not present it in this thesis.
Finally, we note that Markov models, while being implemented in SMPyBandits, are not used in this thesis.
They were introduced in the 1980s, by Whittle in \cite{Whittle1988} and Anantharam and others in \cite{Anantharam87b}.
A Markov MAB model maps an arm to a Markov chain \cite{Norris98}, instead of a distribution, and thus they are no longer stochastic nor stationary.
Such Markov models come in two flavors: rested or restless.
For $K$ arms, each Markov chain has a finite number of states $s$, each corresponding to a (constant) reward that the player obtains if she selects this arm while its Markov chain is in state $s$.
Rested Markov models means that only the state of the selected arm's Markov chain can change, following its Markov transition matrix.
Restless models remove this hypothesis, making them harder to track and solve.
%
Such models were less studied than stationary or adversarial models, but some interesting works focussed on Markov models in the last 10 years\footnote{~
For instance, \cite{Melian15} proposed a cognitive radio model mixing MAB and Hidden Markov Models (HMM), solved by a mixed policy called UCB-HMM.}.
A curious reader about Markov chains could start to read Chapter~3 of \cite{LattimoreBanditAlgorithmsBook} (Section~3.2) and then refer to the famous book \cite{Norris98}.

@@

\paragraph{Problem-dependent lower-bound in $\Omega(\log T)$.}
%
The following two theorems were proven in \cite{LaiRobbins85}.
These lower-bounds are of highest interest to design efficient algorithms,
and a significant part of the research literature on MAB algorithms has focussed on finding algorithms that matches the Lai and Robbins' lower-bound asymptotically.
This means that an upper-bound is proven on the regret of algorithm $\cA$, that asymptotically matches the lower-bound, with the same constant in the big-$\cO$ notation (in which case we say that the algorithm is \emph{optimal}), or with a larger constant (the algorithm is said to be \emph{order-optimal} in such case).

@@

\paragraph{Possible future works.}
%
We focussed in this thesis on finite-arms and one-dimensional bandit problems,
and thus two possible directions of future works could be to extend our works
to MAB models with either multidimensional rewards, like contextual bandits, or infinite arms, like Lipschitz bandits.

>>>>

\paragraph{About Markov models.}
%
% Markov models: we do not present it in this thesis.
Finally, we note that Markov models, while being implemented in SMPyBandits, are not used in this thesis.
They were introduced in the 1980s, by Whittle in \cite{Whittle1988} and Anantharam and others in \cite{Anantharam87b}.
A Markov MAB model maps an arm to a Markov chain \cite{Norris98}, instead of a distribution, and thus they are no longer stochastic nor stationary.
Such Markov models come in two flavors: rested or restless.
For $K$ arms, each Markov chain has a finite number of states $s$, each corresponding to a (constant) reward that the player obtains if she selects this arm while its Markov chain is in state $s$.
Rested Markov models means that only the state of the selected arm's Markov chain can change, following its Markov transition matrix.
Restless models remove this hypothesis, making them harder to track and solve.
%
Such models were less studied than stationary or adversarial models, but some interesting works focused on Markov models in the last 10 years\footnote{~
For instance, \cite{Melian15} proposed a cognitive radio model mixing MAB and Hidden Markov Models (HMM), solved by a mixed policy called UCB-HMM.}.
A curious reader about Markov chains could start to read Chapter~3 of \cite{LattimoreBanditAlgorithmsBook} (Section~3.2) and then refer to the famous book \cite{Norris98}.

@@

\paragraph{Problem-dependent lower-bound in $\Omega(\log T)$.}
%
The following two theorems were proven in \cite{LaiRobbins85}.
These lower-bounds are of highest interest to design efficient algorithms,
and a significant part of the research literature on MAB algorithms has focused on finding algorithms that matches the Lai and Robbins' lower-bound asymptotically.
This means that an upper-bound is proven on the regret of algorithm $\cA$, that asymptotically matches the lower-bound, with the same constant in the big-$\cO$ notation (in which case we say that the algorithm is \emph{optimal}), or with a larger constant (the algorithm is said to be \emph{order-optimal} in such case).

@@

\paragraph{Possible future works.}
%
We focused in this thesis on finite-arms and one-dimensional bandit problems,
and thus two possible directions of future works could be to extend our works
to MAB models with either multidimensional rewards, like contextual bandits, or infinite arms, like Lipschitz bandits.

### 2019-06-12 2-Chapters/3-Chapter/chapter3.tex
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

We focussed here on the most well known algorithms, discussed in Section~\ref{sec:2:famousMABalgorithms}, and two others that are efficient but less known (AdBandits and BESA).
To highlight that SMPyBandits implements many other MAB algorithms proposed in recent works, we detail in Appendix~\ref{sub:3:additionalExperiments} $7$ other algorithms.
They are more recent (some from $2016$, $3$ from $2018$ and $2$ from early $2019$) and are usually more complex, or are based on a different point-of-view.
The numerical results presented below include these extra algorithms, to justify empirically that despite their respective qualities, and despite being very efficient, it is reasonable to focus on \UCB{} and \klUCB{} in the rest of this thesis, as they stay comparable with the state-of-the-art algorithms but are simpler to implement (\eg, when comparing \UCB{} to \texttt{ApproximatedFHGittins} or $\mathrm{MOSS}$-$\mathrm{Anytime}$) to manipulate theoretically (\eg, when comparing \klUCB{} to BESA, PHE or RCB).

>>>>

We focused here on the most well known algorithms, discussed in Section~\ref{sec:2:famousMABalgorithms}, and two others that are efficient but less known (AdBandits and BESA).
To highlight that SMPyBandits implements many other MAB algorithms proposed in recent works, we detail in Appendix~\ref{sub:3:additionalExperiments} $7$ other algorithms.
They are more recent (some from $2016$, $3$ from $2018$ and $2$ from early $2019$) and are usually more complex, or are based on a different point-of-view.
The numerical results presented below include these extra algorithms, to justify empirically that despite their respective qualities, and despite being very efficient, it is reasonable to focus on \UCB{} and \klUCB{} in the rest of this thesis, as they stay comparable with the state-of-the-art algorithms but are simpler to implement (\eg, when comparing \UCB{} to \texttt{ApproximatedFHGittins} or $\mathrm{MOSS}$-$\mathrm{Anytime}$) to manipulate theoretically (\eg, when comparing \klUCB{} to BESA, PHE or RCB).

### 2019-06-12 2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

\textbf{Using another bandit policy?}
%
% Similarly, Philippe Mary asked me at the MoTION workshop where I presented \cite{Bonnefoi2019WCNC}, why didn't we rather used Bayes-UCB instead of \UCB{} (from \cite{Kaufmann12BUCB}), as it is known to empirically outperform \UCB{} (as illustrated for instance in \cite{darak2016bayesian,kumar2016two}).
We could have chose any bandit algorithm for the ``first stage'' component used in this Section, and for simplicity and clarity we focussed on a simple but efficient one (\UCB).
We believe that the same empirical results, but more importantly, the same conclusions, could be given if we used Bayes-UCB or other bandit algorithm for the base building block in the different heuristics proposed in this section.
% ~\ref{sub:43:heuristics}.
Our goal here was not to optimize on the bandit policy (as we presented in Section~\ref{sec:3:reviewSPAlgorithms} some numerical simulations doing precisely this), but rather to compare the different heuristics, for a fixed bandit policy (for which we preferred to use \UCB{} for simplicity).

>>>>

\textbf{Using another bandit policy?}
%
% Similarly, Philippe Mary asked me at the MoTION workshop where I presented \cite{Bonnefoi2019WCNC}, why didn't we rather used Bayes-UCB instead of \UCB{} (from \cite{Kaufmann12BUCB}), as it is known to empirically outperform \UCB{} (as illustrated for instance in \cite{darak2016bayesian,kumar2016two}).
We could have chose any bandit algorithm for the ``first stage'' component used in this Section, and for simplicity and clarity we focused on a simple but efficient one (\UCB).
We believe that the same empirical results, but more importantly, the same conclusions, could be given if we used Bayes-UCB or other bandit algorithm for the base building block in the different heuristics proposed in this section.
% ~\ref{sub:43:heuristics}.
Our goal here was not to optimize on the bandit policy (as we presented in Section~\ref{sec:3:reviewSPAlgorithms} some numerical simulations doing precisely this), but rather to compare the different heuristics, for a fixed bandit policy (for which we preferred to use \UCB{} for simplicity).

### 2019-06-12 2-Chapters/4-Chapter/chapter4.tex
Commentaires de Xtof pour le Ch4
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

% \TODOL{Intégrer les derniers commentaires de Christophe}

% FIXME finish !
\paragraph{Abstract.}
%
In this Chapter~\ref{chapter:4}, we propose two models of Internet of Things (IoT) networks, composed of many independent IoT end-devices,
that can use low-cost RL (Reinforcement Learning) algorithms to learn to improve their spectrum access.
%
Decentralized RL for IoT lets the devices use acknowledgements sent by their Base Station as a reward, instead of sensing feedback like for OSA.
We consider many independent ``dynamic'' devices, communicating with a small probability at every instant.
Simulations show that dynamic devices can improve their spectrum efficiency,
by using MAB algorithms like \UCB.
% in the case of a non-uniform repartition of the static devices in the channels
We also developed a proof-of-concept using USRP platforms, for a real-world validation of this approach.
% Numerical simulations justify the interest of the approach,
%  of the advantage of using MAB algorithms for the first model.
%
% On a simple example, we present in Section~\ref{sec:4:gnuradio} a demonstration that implements and validates the proposed approach, using real wireless radio hardware.
The first model
% without retransmission of packets,
is interesting for its simplicity,
and because considering no retransmission can improve the battery life of IoT devices, at the cost of a lower Quality of Service (QoS).

However, in case of failed transmission of a message, a dynamic device can also retransmit it up-to a fixed number of retransmission (\eg, $M=10$).
We compare different heuristics, based on \UCB, and numerical simulations confirm that the non-naive heuristics significantly improve the network efficiency.
% Interestingly, the simplest heuristic is found to be the most efficient one, as its simplicity implies a faster learning and convergence time.
%
The second model is more interesting if the main target is an improvement of the QoS, rather than a longer battery life.

@@

To sum-up, we focussed in this chapter on models of IoT networks, and we proposed to use classical stationary multi-armed bandit learning algorithms implemented in a selfish and decentralized manner by each of the dynamic devices of the IoT network.
We presented two models of wireless IoT network without sensing, inspired by the ALOHA protocol, and with or without retransmission of uplink packages in case of collisions.
In both cases, we try to model the existing standards, like the LoRa standard, and we demonstrated the efficiency of the proposed MAB-based approach in both numerical simulations and empirical measurements on real wireless radio signals.

>>>>

\paragraph{Abstract.}
%
In this Chapter~\ref{chapter:4}, we propose two models of Internet of Things (IoT) networks, composed of many independent IoT end-devices,
that can use low-cost RL (Reinforcement Learning) algorithms to learn to improve their spectrum access.
%
Decentralized RL for IoT lets the devices use acknowledgements sent by their Base Station as a reward, instead of sensing feedback like for OSA.
We consider many independent ``dynamic'' devices, communicating with a small probability at every instant.
Simulations show that dynamic devices can improve their spectrum efficiency,
by using MAB algorithms like \UCB.
% in the case of a non-uniform repartition of the static devices in the channels
We also developed a proof-of-concept using USRP platforms, for a real-world validation of this approach.
% Numerical simulations justify the interest of the approach,
%  of the advantage of using MAB algorithms for the first model.
%
% On a simple example, we present in Section~\ref{sec:4:gnuradio} a demonstration that implements and validates the proposed approach, using real wireless radio hardware.
The first model
% without retransmission of packets,
is interesting for its simplicity,
and because considering no retransmission can improve the battery life of IoT devices, at the cost of a lower Quality of Service (QoS).

However, in case of failed transmission of a message, a dynamic device can also retransmit it up-to a fixed number of retransmission.
We compare different heuristics, based on \UCB, and numerical simulations confirm that the non-naive heuristics significantly improve the network efficiency.
% Interestingly, the simplest heuristic is found to be the most efficient one, as its simplicity implies a faster learning and convergence time.
%
The second model is more interesting if the main target is an improvement of the QoS, rather than a longer battery life.

@@

To sum-up, we focused in this chapter on models of IoT networks, and we proposed to use classical stationary multi-armed bandit learning algorithms implemented in a selfish and decentralized manner by each of the dynamic devices of the IoT network.
We presented two models of wireless IoT network without sensing, inspired by the ALOHA protocol, and with or without retransmission of uplink packages in case of collisions.
In both cases, we try to model the existing standards, like the LoRa standard, and we demonstrated the efficiency of the proposed MAB-based approach in both numerical simulations and empirical measurements on real wireless radio signals.

### 2019-06-12 2-Chapters/5-Chapter/chapter5.tex
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

Finally, we note that previous works all focussed on the ``sensing'' case, but most likely sub-linear regret can be achieve by decentralized algorithms that leverage the same techniques as introduced by \cite{BoursierPerchet18,LugosiMehrabian18} for the ``no sensing case''.
%
We conclude by noting that this model was recently studied by two very recent other works, \cite{DarakHanawal18,Tibrewal2019}, who obtained results comparable to the results from the two works presented above.
They both also study the case of dynamic settings, with arrival or departures of players, as presented in Section~\ref{sub:5:arrivalDepartures}.
Both articles \cite{DarakHanawal18,Tibrewal2019} use the terminology of ad-hoc networks, and they compare empirically their proposal with some previous works, while \cite{KaufmannAbbas19} do not include numerical simulations, and while \cite{Bistritz18} illustrate the performance of their GoT algorithm on a simple example, they do not compare with other algorithms.
%
It would be interesting to compare empirically all the different approaches.
Another interesting directions are to study the possible extension of this model with different arm utilities by players to the non-stationary case, or real-world validation of such decentralized algorithms in real IoT networks.

@@

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focussed on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $[M]$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn,
% \footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.},
where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
We include different \rhoLearn{} algorithms, that uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multiple-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.

@@

Since the beginning of this thesis, all the studied bandit problems were stationary: the rewards coming from choosing arm $k$ are \iid{} and follow the same distribution $\nu_k$.
The next Chapter~\ref{chapter:6} is focussed on the piece-wise stationary bandit model, a relaxation of this hypothesis.

>>>>

Finally, we note that previous works all focused on the ``sensing'' case, but most likely sub-linear regret can be achieve by decentralized algorithms that leverage the same techniques as introduced by \cite{BoursierPerchet18,LugosiMehrabian18} for the ``no sensing case''.
%
We conclude by noting that this model was recently studied by two very recent other works, \cite{DarakHanawal18,Tibrewal2019}, who obtained results comparable to the results from the two works presented above.
They both also study the case of dynamic settings, with arrival or departures of players, as presented in Section~\ref{sub:5:arrivalDepartures}.
Both articles \cite{DarakHanawal18,Tibrewal2019} use the terminology of ad-hoc networks, and they compare empirically their proposal with some previous works, while \cite{KaufmannAbbas19} do not include numerical simulations, and while \cite{Bistritz18} illustrate the performance of their GoT algorithm on a simple example, they do not compare with other algorithms.
%
It would be interesting to compare empirically all the different approaches.
Another interesting directions are to study the possible extension of this model with different arm utilities by players to the non-stationary case, or real-world validation of such decentralized algorithms in real IoT networks.

@@

In \cite{darak2016bayesian,Darak16}, the authors study the same model and focused on the \RhoRand{} policy, which was the state-of-the-art back in $2016$, combined with \UCB{} or \klUCB, as well as an extension using Bayes-UCB from \cite{Kaufmann12BUCB}.
Their idea is to use the same skeleton as \RhoRand, that is to assign a \emph{rank} to each player, and make players change their rank after any collision. But instead of selecting a new rank uniformly at random among $[M]$, they proposed to use a ``second-stage'' learning policy\footnote{This is a very natural idea: use a bandit algorithm to balance the exploration/exploitation aspect of rank selection, instead of a random hoping.}, based on Bayes-UCB, to (try to) learn the best rank while still exploring each rank from time to time.
This algorithm is implemented in SMPyBandits and named \rhoLearn,
% \footnote{See \href{https://smpybandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}{\texttt{SMPyBandits.github.io/docs/PoliciesMultiPlayers.rhoLearn.html}} for its documentation.},
where it can use Bayes-UCB or any of the $65$ or more bandit algorithms available in the library.
Even if no theoretical guarantee backs up this idea of second-stage learning with Bayes-UCB, empirical simulations found that it can be efficient.
We illustrate this in Table~\ref{table:5:comparisonRhoRandRhoLearn} below, where we consider the same problem as described above in Section~\ref{sub:5:withoutSensing} (Table~\ref{table:5:meanRegretSimulationsNoSensing}).
We include different \rhoLearn{} algorithms, that uses \klUCB{}, Bayes-UCB or Exp3 for the second-stage learning,
and we include both the centralized multiple-play version of \klUCB{} and \MCTopM-\klUCB{} for comparison.

@@

Since the beginning of this thesis, all the studied bandit problems were stationary: the rewards coming from choosing arm $k$ are \iid{} and follow the same distribution $\nu_k$.
The next Chapter~\ref{chapter:6} is focused on the piece-wise stationary bandit model, a relaxation of this hypothesis.

### 2019-06-12 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

% Stochastic bandits were historically introduced as a simple model for clinical trials, where arms correspond to some treatments with unknown efficacy \cite{Thompson33}.
% More recently, MAB models have been proven useful for different applications, like cognitive radio, where arms can model the vacancy of radio channels, as presented in Chapter~\ref{chapter:4}, or parameters of a dynamically configurable radio hardware \cite{Maghsudi16,Bonnefoi17,KerkoucheAlami18}.
% Another application is the design of recommender systems, where arms model the popularity of different items (\eg, news recommendation, \cite{Li10}).
%
For cognitive radio applications, as well as other applications such as recommender systems, the assumption that the arms distribution \emph{do not change over time} may be a big limitation.
Indeed, in cognitive radio, new devices can enter or leave the network, which impacts the availability of the radio channel they use to communicate.
And for instance in online recommendation, the popularity of items is also subject to trends.
Hence, there has been some interest on how to take those \emph{non-stationary} aspects into account within a multi-armed bandit model.

@@

It could seem that the problem is considered as solved by the Exp3.S algorithm, but it was actively studied since the seminal paper \cite{Auer02NonStochastic}.
Two main reasons explain the dynamic research on this problem:
first, it is well known that despite their qualities, exponential-weights algorithms like Exp3 can usually be greatly outperformed by UCB-based algorithms, for stochastic problems, and so it is expected that Exp3.S can be outperformed by other algorithms, thus any practical application might benefit from algorithms more efficient than Exp3.S.
%
The second reason is that passively adaptive algorithms function as black-box models: they do not try to detect changes and do not explain why they changed from one arm to another. A lot of the recent research has been focussed on actively adaptive algorithms, precisely because they allow to interpret their decisions, by detecting changes on arms with statistical tests.
The piece-wise stationary MAB model was then studied by \cite{Kocsis06} and \cite{YuMannor09}.
%
This model is sometimes referred to as the abruptly changing \cite{WeiSrivastava18Abruptly}, or switching environments \cite{MellorShapiro13}.
%
In this model, described in full details in Section~\ref{sec:6:BanditSetting}, the (random) reward of arm $k$ at round $t$ has some mean $\mu_k(t)$, that is constant on intervals between two \emph{breakpoints}, and the regret is measured with respect to the \emph{current} best arm $k_t^* = \arg\max_i \mu_k(t)$.

@@

\paragraph{About \klUCB.}
%
Our proposal \GLRklUCB{} is inspired by both the \MUCB{} and \CUSUMUCB{} algorithms.
Previous works focussed on using \UCB{} \cite{LiuLeeShroff17,CaoZhenKvetonXie18},
but we propose to use \klUCB{} instead, as it is known to be more efficient for Bernoulli rewards as well as for a more generic case of bounded or one-dimensional exponential families \cite{KLUCBJournal}.
Theoretical results for these works were only given for \UCB, but they both suggest that extending the results to \klUCB{} (or other efficient stationary policies) should not be difficult.
For a fair comparison, we therefore chose to compare the different change-point detector algorithms combined with \klUCB.
We also include in Table~\ref{table:6:comparisonUCB_klUCB} a comparison of the performance of different algorithms when using \UCB{} or \klUCB{} indexes, to illustrate that using a more efficient index policy always improves performance, as predicted.

>>>>

% Stochastic bandits were historically introduced as a simple model for clinical trials, where arms correspond to some treatments with unknown efficacy \cite{Thompson33}.
% More recently, MAB models have been proven useful for different applications, like cognitive radio, where arms can model the vacancy of radio channels, as presented in Chapter~\ref{chapter:4}, or parameters of a dynamically configurable radio hardware \cite{Maghsudi16,Bonnefoi17,KerkoucheAlami18}.
% Another application is the design of recommender systems, where arms model the popularity of different items (\eg, news recommendation, \cite{Li10}).
%
For cognitive radio applications, as well as other applications such as recommender systems, the assumption that the arms distribution \emph{do not change over time} may be a big limitation.
Indeed, in cognitive radio and IoT networks, new devices can enter or leave the network, which impacts the availability of the radio channel they use to communicate.
And for instance in online recommendation, the popularity of items is also subject to trends.
Hence, there has been some interest on how to take those \emph{non-stationary} aspects into account within a multi-armed bandit model.

@@

It could seem that the problem is considered as solved by the Exp3.S algorithm, but it was actively studied since the seminal paper \cite{Auer02NonStochastic}.
Two main reasons explain the dynamic research on this problem:
first, it is well known that despite their qualities, exponential-weights algorithms like Exp3 can usually be greatly outperformed by UCB-based algorithms, for stochastic problems, and so it is expected that Exp3.S can be outperformed by other algorithms, thus any practical application might benefit from algorithms more efficient than Exp3.S.
%
The second reason is that passively adaptive algorithms function as black-box models: they do not try to detect changes and do not explain why they changed from one arm to another. A lot of the recent research has been focused on actively adaptive algorithms, precisely because they allow to interpret their decisions, by detecting changes on arms with statistical tests.
The piece-wise stationary MAB model was then studied by \cite{Kocsis06} and \cite{YuMannor09}.
%
This model is sometimes referred to as the abruptly changing \cite{WeiSrivastava18Abruptly}, or switching environments \cite{MellorShapiro13}.
%
In this model, described in full details in Section~\ref{sec:6:BanditSetting}, the (random) reward of arm $k$ at round $t$ has some mean $\mu_k(t)$, that is constant on intervals between two \emph{breakpoints}, and the regret is measured with respect to the \emph{current} best arm $k_t^* = \arg\max_i \mu_k(t)$.

@@

\paragraph{About \klUCB.}
%
Our proposal \GLRklUCB{} is inspired by both the \MUCB{} and \CUSUMUCB{} algorithms.
Previous works focused on using \UCB{} \cite{LiuLeeShroff17,CaoZhenKvetonXie18},
but we propose to use \klUCB{} instead, as it is known to be more efficient for Bernoulli rewards as well as for a more generic case of bounded or one-dimensional exponential families \cite{KLUCBJournal}.
Theoretical results for these works were only given for \UCB, but they both suggest that extending the results to \klUCB{} (or other efficient stationary policies) should not be difficult.
For a fair comparison, we therefore chose to compare the different change-point detector algorithms combined with \klUCB.
We also include in Table~\ref{table:6:comparisonUCB_klUCB} a comparison of the performance of different algorithms when using \UCB{} or \klUCB{} indexes, to illustrate that using a more efficient index policy always improves performance, as predicted.

### 2019-06-12 2-Chapters/Conclusion/conclusion.tex
Focussed -> focused. Okay... http://www.future-perfect.co.uk/grammar-tip/is-it-focussed-or-focused/

As detailed in Chapter~\ref{chapter:2}, we focussed in this thesis on finite-arms and one-dimensional bandit problems,
and thus two possible directions of future research could be to extend our works
to MAB models with either multidimensional rewards, like contextual bandits, or infinite arms, like Lipschitz bandits.
The hypotheses we made were motivated by the target applications, but these other models have also started to be used for cognitive radio applications.

>>>>

As detailed in Chapter~\ref{chapter:2}, we focused in this thesis on finite-arms and one-dimensional bandit problems,
and thus two possible directions of future research could be to extend our works
to MAB models with either multidimensional rewards, like contextual bandits, or infinite arms, like Lipschitz bandits.
The hypotheses we made were motivated by the target applications, but these other models have also started to be used for cognitive radio applications.
